\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Edge Computing vs. Cloud Computing: Trade-offs in Latency, Privacy, and Scalability 
}

\author{\IEEEauthorblockN{Thaddeus Salwan}
\IEEEauthorblockA{\textit{John Carroll University} \\
Cleveland, United States \\
tsalwan26@jcu.edu}
\and

\IEEEauthorblockN{Stephen Loya}
\IEEEauthorblockA{\textit{John Carroll University} \\
Cleveland, United States \\
sloya25@jcu.edu}
\and

\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
City, Country \\
email address or ORCID}
\and

\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
City, Country \\
email address or ORCID}
\and

}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
Edge Computing, Cloud Computing, latency, privacy, security
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits. 

\section{An Overview of Edge Computing}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{An Overview of Cloud Computing}
Cloud Computing can best be described as a “computing model that enables on-demand access to a shared pool of configurable computing resources, such as servers, storage, and applications, over the internet” [2]. Cloud Computing resources are located off-site, usually in large data centers managed by a Cloud Service Provider (CSP)[2]. There are three common cloud service models offered to tenants. The first is Infrastructure as a Service (IaaS). IaaS provides tenants with hardware resources and infrastructure as well as a virtual interface to interact with those resources. The tenant uses its own operating system. A step up in service is Platform as a Service. PaaS provides the tenant with everything that is included in the IaaS model along with a base operating system and some development tools. This is mainly used for application development and deployment. The last model, Software as a Service (SaaS) fully provides the hardware resources, operating systems, and applications [6]. These Cloud Computing service models allow companies to focus on their business operations and product instead of computational infrastructure and resource management.
The greatest strength of Cloud Computing is its tremendous scalability. Most services offer “on-demand self-service” [2]; resources are automatically scaled and distributed across machines to handle workload without needing manual input from the CSP. Pairing this with pay-as-you-go pricing allows companies to effectively manage the IT related aspects of their business effortlessly while only paying for what they actually use. Even with great benefits, Cloud Computing still has shortcomings such as high latency and bandwidth consumption [2]. Data must be transferred between the tenant and the data center, which often miles away from each other, for storage or processing. Cloud Computing helps companies focus on their business instead of IT resources by offering highly scalable and flexible hardware resources, but with a cost of high latency.

\section{Edge Computing vs. Cloud Computing: Latency}
Start typing here

\section{Edge Computing vs. Cloud Computing: Privacy}
Start typing here

\section{Edge Computing vs. Cloud Computing: Scalability}
Edge Computing vs. Cloud Computing: Scalability - Tad
Scalability is a major strength of both Edge Computing and Cloud Computing. Both methods of computing work similarly, allowing for resources to be easily scalable. Edge Computing allows for quick scalability and distribution of workload across multiple edge nodes [2]. However, Edge Computing has limited resources for computation and also requires that an Edge Computing center be in a specific geographic location that is close to the data source and on the edge of the network. In some instances, this might require an Edge Computing center be built. This can be a costly process, especially in areas that are hard to reach and build in [2]. Cloud Computing allows access to vast resources located in large data centers. Similarly to Edge Computing, Cloud Computing will automatically scale up or down depending on what the tenant needs, while also doing it on a significantly larger scale. It also allows for automatic distribution of workloads across multiple nodes [2].
Big Data Analysis is one of the primary uses of Edge and Cloud Computing [5]. Cloud Computing can scale to a tremendous extent, allowing for enormous amounts of data to be processed and stored in data centers. There are enough hardware resources located in data centers that can automatically scale to handle data sets of any size. Edge Computing, due to hardware limitations, does not have the ability to scale up resources to handle the large amounts of data collected from data sources. In this situation, Edge Computing is useful for collection and quick processing of data close to the data source, but needs to then pass on this data to data centers where Cloud Computing can handle the Big Data Analysis [5].

\section{Integrating Cloud Computing and Edge Computing Together}
Start typing here

\section{Conclusion}
Start typing here

\begin{thebibliography}{00}
\bibitem{b1}@article{varghese2017edge,
	title={Edge-as-a-service: Towards distributed cloud architectures},
	author={Varghese, Blesson and Wang, Nan and Li, Jianyu and Nikolopoulos, Dimitrios S},
	journal={arXiv preprint arXiv:1710.10090},
	year={2017}
}
\bibitem{b2}@article{george2023edge,
	title={Edge computing and the future of cloud computing: A survey of industry perspectives and predictions},
	author={George, A Shaji and George, AS Hovan and Baskar, T},
	journal={Partners Universal International Research Journal},
	volume={2},
	number={2},
	pages={19--44},
	year={2023}
}
\bibitem{b3}@article{khan2019edge,
	title={Edge computing: A survey},
	author={Khan, Wazir Zada and Ahmed, Ejaz and Hakak, Saqib and Yaqoob, Ibrar and Ahmed, Arif},
	journal={Future Generation Computer Systems},
	volume={97},
	pages={219--235},
	year={2019},
	publisher={Elsevier}
}
\bibitem{b4}@article{shi2016edge,
	title={Edge computing: Vision and challenges},
	author={Shi, Weisong and Cao, Jie and Zhang, Quan and Li, Youhuizi and Xu, Lanyu},
	journal={IEEE internet of things journal},
	volume={3},
	number={5},
	pages={637--646},
	year={2016},
	publisher={IEEE}
}
\bibitem{b5}@article{bajic2019edge,
	title={EDGE COMPUTING VS. CLOUD COMPUTING: CHALLENGES AND OPPORTUNITIES IN INDUSTRY 4.0.},
	author={Bajic, Bojana and Cosic, Ilija and Katalinic, Branko and Moraca, Slobodan and Lazarevic, Milovan and Rikalovic, Aleksandar},
	journal={Annals of DAAAM \& Proceedings},
	volume={30},
	year={2019}
}
\bibitem{b6}@article{parikh2019security,
	title={Security and privacy issues in cloud, fog and edge computing},
	author={Parikh, Shalin and Dave, Dharmin and Patel, Reema and Doshi, Nishant},
	journal={Procedia Computer Science},
	volume={160},
	pages={734--739},
	year={2019},
	publisher={Elsevier}
}
\end{thebibliography}

\end{document}